Intelligence and Age at First Intercourse: Cause or Confound?

### 2015-08-05 afidraftRnw.tex
AFI

\section{Methods}\cmb{content/methods.txt}\input{content/methods.txt}
<<setup, include=FALSE>>=
file_drive= "C:"
#file_drive="E:"
#Libraries

library(devtools);dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("ggplot2")#dev_mode(on=F) 
#install_github("harrelfe/Hmisc")
library(knitr)
library(ggplot2)
library(effects)
library(stargazer)
library(NlsyLinks)
library(plyr)
library(tables)
library(Hmisc)
library(MplusAutomation)
library(WrightMap)
#Functions
####### FUNCTIONS #######
source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")

#OPtions
options(scipen=999)
options(digits=3)
options(width=60)
opts_chunk$set(fig.path='figure/beamer-',fig.align='center',fig.show='hold',size='footnotesize')

#Data_9
LinkedMDAN_discord_AFI_z_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_910811.csv",sep=""))
LinkedMDAN_discord_AFI_z_9$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_9$Gendermean)
LinkedMDAN_discord_AFI_g_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_910811.csv",sep=""))
LinkedMDAN_discord_AFI_b_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_910811.csv",sep=""))

#Models_9
data=LinkedMDAN_discord_AFI_z_9
model.meankids_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_9<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_9

model.meankids.g_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_9<-anova(model.diffkids.g.nested_9,model.diffkids.g.full_9)
model.diffmoms.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_9
model.meankids.b_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_10
LinkedMDAN_discord_AFI_z_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_z_10$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_10$Gendermean)
LinkedMDAN_discord_AFI_g_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_b_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_1011912.csv",sep=""))

#Models_10
data=LinkedMDAN_discord_AFI_z_10
model.meankids_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_10<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_10

model.meankids.g_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_10<-anova(model.diffkids.g.nested_10,model.diffkids.g.full_10)
model.diffmoms.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_10
model.meankids.b_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_11
LinkedMDAN_discord_AFI_z_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_z_11$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_11$Gendermean)
LinkedMDAN_discord_AFI_g_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_b_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_11121013.csv",sep=""))
data=LinkedMDAN_discord_AFI_z_11

#Models_11
model.meankids_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.int_11<-lm(Int_Mean ~ INTMOMmean, data = data)
model.meanmoms_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.diffkids_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean +INTMOMmean + Intdiff+  INTMOMdiff, data = data)
model.meanmomskids_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffmomsint_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff + Gendermean + INTMOMmean:Gendermean, data = data)
data=LinkedMDAN_discord_AFI_g_11

model.meankids.g_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_11<-anova(model.diffkids.g.nested_11,model.diffkids.g.full_11)
model.diffmoms.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_11
model.meankids.b_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#summarystats
birthweight <- read.table(paste(file_drive,"/Dropbox/SAS/MyFolders/79/SASGen1Kids/birthweight.dat",sep=""), quote="\"", stringsAsFactors=FALSE)
names(birthweight)<-c('CASEID','MCASEID','RACE','SEX_G2','YRB','WGT')
birthweight$WGT[birthweight$WGT < 0] <- NA
birthweight$firstborn<-0
birthweight$firstborn<-substrRight(birthweight$CASEID,2)
birthweight_2<-birthweight
birthweight$born[birthweight$firstborn!="01"]<-0
birthweight$born[birthweight$firstborn=="01"]<-1
birthweight_fb <- birthweight[ which(birthweight$born==1), ]

new_data <- read.table('gen2demographics.dat', sep=' ')
names(new_data) <- c('C0000100','C0000200','C0005300','C0005400')

# Handle missing values
  new_data[new_data == -1] = NA  # Refused 
  new_data[new_data == -2] = NA  # Dont know 
  new_data[new_data == -3] = NA  # Invalid missing 
  new_data[new_data == -7] = NA  # Missing

# If there are values not categorized they will be represented as NA
vallabels = function(data) {
 # data$C0000100 <- cut(data$C0000100, c(1.0,9999999.0), labels=c("1 TO 9999999: See Min & Max values below for range as of this release"), right=FALSE)
#  data$C0000200 <- cut(data$C0000200, c(1.0,12686.0), labels=c("1 TO 12686: NLSY79 Public ID"), right=FALSE)
  data$C0005300 <- factor(data$C0005300, levels=c(1.0,2.0,3.0), labels=c("HISPANIC","BLACK","NON-BLACK, NON-HISPANIC"))
  data$C0005400 <- factor(data$C0005400, levels=c(1.0,2.0), labels=c("MALE","FEMALE"))
  return(data)
}

varlabels <- c(    "ID CODE OF CHILD",
    "ID CODE OF MOTHER OF CHILD",
    "RACE OF CHILD (FROM MOTHERS SCREENER 79)",
    "SEX OF CHILD"
)

qnames = function(data) {
  names(data) <- c("CASEID","MCASEID","RACE","CSEX")
  return(data)
}

categories_g2 <- qnames(vallabels(new_data))

momintel <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/79/SASGen1/momintel.csv",sep=""), header=FALSE)
names(momintel)<-c("MCASEID","Intel_G1","Intel_G1_SE","HID")
#momintel$zIntel_G1<-scale(momintel$Intel_G1, center = TRUE, scale = TRUE)*15+100

kidintel<-read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(kidintel)<-c("CASEID","ASEID","Intel_G2","Intel_G2_SE","MCASEID")
#kidintel$zIntel_G2<-scale(kidintel$Intel_G2, center = TRUE, scale = TRUE)*15+100
Gen1AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/Gen1AFI_exportconcor_910811.csv",sep=""))
Gen1AFI_exportconcor <- Gen1AFI_exportconcor[2:length(Gen1AFI_exportconcor[,1]),]
names(Gen1AFI_exportconcor)<-c("MCASEID","AFI_G1")
Gen2AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/Gen2AFI_exportconcor_910811.csv",sep=""))
names(Gen2AFI_exportconcor)<-c("CASEID","AFI_G2")

Gen1AFIConcor <- merge(momintel,Gen1AFI_exportconcor,by="MCASEID",all=T)
Gen2AFIConcor <- merge(kidintel,Gen2AFI_exportconcor,by="CASEID",all=T)
Gen2AFIConcor_2 <- merge(categories_g2,Gen2AFI_exportconcor,by="CASEID",all=T)

@
<<measurement,include=FALSE>>=
#G1
#runModels(directory =paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG1",sep=""))
ModelSummaries_Mplus<-extractModelSummaries(target = paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG1",sep=""))
ModelSummaries_Mplus[,4]<-NULL;ModelSummaries_Mplus[,3]<-NULL;ModelSummaries_Mplus[,2]<-NULL;ModelSummaries_Mplus[,1]<-NULL;ModelSummaries_Mplus[,23]<-NULL
capture.output(stargazer(ModelSummaries_Mplus,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_gen1measurement.tex",sep=""))

##irt plots

IRT2PL_person <- read.table(paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG1/IRT2PL_person.csv",sep=""), quote="\"")
thresholdsw <- read.csv(paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG1/thresholdsw.csv",sep=""), stringsAsFactors=FALSE)
itemshapes <- thresholdsw[,7]
itemcolors <- thresholdsw[,6]
labelitems <-thresholdsw[,1]
labelitems2<-c(1:length(thresholdsw[,1]))
thetas<-sqrt(1.6)*IRT2PL_person$V106; thresholds<-sqrt(1.6)*thresholdsw[,2]
png(filename=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/G1wrightMap.png",sep=""),width = 750, height = 500)
wrightMap(thetas, thresholds,show.thr.lab = TRUE,
    use.hist = FALSE,thr.sym.col.fg = itemcolors,thr.sym.pch = itemshapes,
    thr.sym.cex = 2.5,thr.lab.text=labelitems,label.items=labelitems2,axis.logits="Logits",dim.names="General Ability",max.logit.pad=.51)
dev.off()
##G2
#runModels(directory =paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG2",sep="")
ModelSummaries_Mplusg2_9<-extractModelSummaries(target = paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG2/g_around_910811.out",sep=""))
g2loading_9 <- read.csv(paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/g2loading_9.csv",sep=""), stringsAsFactors=FALSE)
g2loading_10 <- read.csv(paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/g2loading_10.csv",sep=""), stringsAsFactors=FALSE)
g2loading_11 <- read.csv(paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/g2loading_11.csv",sep=""), stringsAsFactors=FALSE)
ModelSummaries_Mplusg2_10<-extractModelSummaries(target = paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG2/g_around_1011912.out",sep=""))
ModelSummaries_Mplusg2_11<-extractModelSummaries(target = paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/MplusG2/g_around_11121013.out",sep=""))
ModelSummaries_Mplusg2_9[,4]<-NULL;ModelSummaries_Mplusg2_9[,3]<-NULL;ModelSummaries_Mplusg2_9[,2]<-NULL;ModelSummaries_Mplusg2_9[,1]<-NULL;ModelSummaries_Mplusg2_9[,26]<-NULL;ModelSummaries_Mplusg2_9[,7]<-NULL;ModelSummaries_Mplusg2_9[,7]<-NULL;ModelSummaries_Mplusg2_9[,7]<-NULL
capture.output(stargazer(ModelSummaries_Mplusg2_9,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2_9measurement.tex",sep=""))
capture.output(stargazer(g2loading_9,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2loading_9.tex",sep=""))

ModelSummaries_Mplusg2_10[,4]<-NULL;ModelSummaries_Mplusg2_10[,3]<-NULL;ModelSummaries_Mplusg2_10[,2]<-NULL;ModelSummaries_Mplusg2_10[,1]<-NULL;ModelSummaries_Mplusg2_10[,26]<-NULL;ModelSummaries_Mplusg2_10[,7]<-NULL;ModelSummaries_Mplusg2_10[,7]<-NULL;ModelSummaries_Mplusg2_10[,7]<-NULL
capture.output(stargazer(ModelSummaries_Mplusg2_10,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2_10measurement.tex",sep=""))
capture.output(stargazer(g2loading_10,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2loading_10.tex",sep=""))

ModelSummaries_Mplusg2_11[,4]<-NULL;ModelSummaries_Mplusg2_11[,3]<-NULL;ModelSummaries_Mplusg2_11[,2]<-NULL;ModelSummaries_Mplusg2_11[,1]<-NULL;ModelSummaries_Mplusg2_11[,26]<-NULL;ModelSummaries_Mplusg2_11[,7]<-NULL;ModelSummaries_Mplusg2_11[,7]<-NULL;ModelSummaries_Mplusg2_11[,7]<-NULL
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2_11measurement.tex",sep=""))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_g2loading_11.tex",sep=""))

@
\cmb{content/Gen1measure.txt}\input{content/Gen1measure.txt}

\cmb{content/Gen2measure.txt}\input{content/Gen2measure.txt}

\section{Results}\cmb{content/results.txt}\input{content/results.txt}
%\subsection{Between vs. Within Illustration}
%\cmb{content/results_meancomp.txt}\input{content/results_meancomp.txt}
<<regressionresults,echo=FALSE, comment=NA, include=FALSE>>=

##9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,font.size="small",no.space=TRUE,#style="demography",
                         column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen1 Intel"), dep.var.labels=c("Mean Gen2 AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex",sep=""))

capture.output(stargazer(model.meankids_9,model.meankids.g_9,model.meankids.b_9,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen2 Intel"), dep.var.labels=c("Mean Gen2 AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci = TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Child_Intelligence_Mean_Child_AFI_9.tex",sep=""))

capture.output(stargazer(model.meanmomskids_9,model.meanmomskids.g_9,model.meanmomskids.b_9,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Mean Gen2 AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE,covariate.labels=c("Gen1 Intel","Gen2 Intel")
                         ),
                         file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Joint_Intelligence_Mean_Child_AFI_9.tex",sep=""))

capture.output(stargazer(model.diffmoms_9,model.diffmoms.g_9,model.diffmoms.b_9,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences"),#covariate.labels=c("Gen2 AFI","Gen1 Intel", "Dif Gen1 Intel"),
                         column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Mom_Intelligence_Dif_Child_AFI_9.tex",sep=""))

capture.output(stargazer(model.diffkids_9,model.diffkids.g_9,model.diffkids.b_9,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences"),#covariate.labels=c("Gen2 AFI","Gen2 Intel", "Dif Gen2 Intel"),
                         column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Child_Intelligence_Dif_Child_AFI_9.tex",sep=""))

capture.output(stargazer(model.diffmomskids_9,model.diffmomskids.g_9,model.diffmomskids.b_9,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Gen2 AFI Differences"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE#,covariate.labels=c("Gen2 AFI","Gen2 Intel","Gen1 Intel","Dif Gen2 Intel","Dif Gen1 Intel")
                         ),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Joint_Intelligence_Dif_Child_AFI_9.tex",sep=""))

## 10.5
capture.output(stargazer(model.meanmoms_10,model.meanmoms.g_10,model.meanmoms.b_10,font.size="small",no.space=TRUE,#style="demography",
                         column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen1 Intel"), dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Mom_Intelligence_Mean_Child_AFI_10.tex",sep=""))

capture.output(stargazer(model.meankids_10,model.meankids.g_10,model.meankids.b_10,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen2 Intel"), dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci = TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Child_Intelligence_Mean_Child_AFI_10.tex",sep=""))

capture.output(stargazer(model.meanmomskids_10,model.meanmomskids.g_10,model.meanmomskids.b_10,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE#,covariate.labels=c("Gen1 Intel","Gen2 Intel")
                         ),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Joint_Intelligence_Mean_Child_AFI_10.tex",sep=""))

capture.output(stargazer(model.diffmoms_10,model.diffmoms.g_10,model.diffmoms.b_10,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences")#,covariate.labels=c("Gen2 AFI","Gen1 Intel", "Dif Gen1 Intel")
                         ,column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Mom_Intelligence_Dif_Child_AFI_10.tex",sep=""))

capture.output(stargazer(model.diffkids_10,model.diffkids.g_10,model.diffkids.b_10,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences")#,covariate.labels=c("Gen2 AFI","Gen2 Intel", "Dif Gen2 Intel")
                         ,column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Child_Intelligence_Dif_Child_AFI_10.tex",sep=""))

capture.output(stargazer(model.diffmomskids_10,model.diffmomskids.g_10,model.diffmomskids.b_10,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Gen2 AFI Differences"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE#,covariate.labels=c("Gen2 AFI","Gen2 Intel","Gen1 Intel","Dif Gen2 Intel","Dif Gen1 Intel")
                         ),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Joint_Intelligence_Dif_Child_AFI_10.tex",sep=""))

##11.5

capture.output(stargazer(model.meanmoms_11,model.meanmoms.g_11,model.meanmoms.b_11,font.size="small",no.space=TRUE,#style="demography",
                         column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen1 Intel"), dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Mom_Intelligence_Mean_Child_AFI_11.tex",sep=""))

capture.output(stargazer(model.meankids_11,model.meankids.g_11,model.meankids.b_11,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,covariate.labels=c("Gen2 Intel"), dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci = TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Child_Intelligence_Mean_Child_AFI_11.tex",sep=""))

capture.output(stargazer(model.meanmomskids_11,model.meanmomskids.g_11,model.meanmomskids.b_11,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Mean AFI"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE#,covariate.labels=c("Gen1 Intel","Gen2 Intel")
                         ),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Mean_Joint_Intelligence_Mean_Child_AFI_11.tex",sep=""))

capture.output(stargazer(model.diffmoms_11,model.diffmoms.g_11,model.diffmoms.b_11,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences"),#covariate.labels=c("Gen2 AFI","Gen1 Intel", "Dif Gen1 Intel"),
                         column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Mom_Intelligence_Dif_Child_AFI_11.tex",sep=""))

capture.output(stargazer(model.diffkids_11,model.diffkids.g_11,model.diffkids.b_11,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE,dep.var.labels=c("Gen2 AFI Differences"),
                         #covariate.labels=c("Gen2 AFI","Gen2 Intel", "Dif Gen2 Intel"),
                         column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Child_Intelligence_Dif_Child_AFI_11.tex",sep=""))

capture.output(stargazer(model.diffmomskids_11,model.diffmomskids.g_11,model.diffmomskids.b_11,font.size="small",no.space=TRUE,column.sep.width = "1pt",header = FALSE, dep.var.labels=c("Gen2 AFI Differences"),column.labels = c("Mixed", "Daughers", "Sons"),model.numbers=FALSE,float=FALSE,ci =TRUE,single.row = FALSE
                         #,covariate.labels=c("Gen2 AFI","Gen2 Intel","Gen1 Intel","Dif Gen2 Intel","Dif Gen1 Intel")
                         ),file=paste(file_drive,"/Dropbox/Work/Research/Projects/NLSY/AFI/R/table_Dif_Joint_Intelligence_Dif_Child_AFI_11.tex",sep=""))

>>>>

\section{Methods}\cmb{content/methods.txt}\input{content/methods.txt}
